Generative Adversarial Networks

### 2017-12-05 cs6735/project/report.tex
done exam notes

\section{Architecture & Training Variations}
Research within the field of deep generative modeling has increased exponentially since the debut of GANs in 2014. Significant improvements have been made with respect to image quality and training stability. Hundreds of papers have been released on the subject of GANs (see figure \ref{fig:CumulativeNumberofGANPapersbyMonth}) which propose numerous architectural and training variations.

>>>>

\section{Architecture \& Training Variations}
Research within the field of deep generative modeling has increased exponentially since the debut of GANs in 2014. Significant improvements have been made with respect to image quality and training stability. Hundreds of papers have been released on the subject of GANs (see figure \ref{fig:CumulativeNumberofGANPapersbyMonth}) which propose numerous architectural and training variations.
